---
title: "BenchmarkStudy"
author: "Tomoya Ozawa"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(MASS)
library(tidyverse)
library(strucchange)
library(segmented)
library(bcp)
```

## Simulated data: One change Point

```{r}
set.seed(123)
X_const <- matrix(rep(1, 100), nrow = 100)
X_1 <- mvrnorm(n = 100, mu = rep(0, 5), Sigma = diag(5))
X_2 <- mvrnorm(n = 100, mu = rep(0, 5), Sigma = diag(5))

X_1 <- cbind(X_const, X_1)
X_2 <- cbind(X_const, X_2)

Beta_1 <- matrix(rep(1, 6), nrow = 6)
Beta_2 <- matrix(c(1, -1, 0, -1, 0, 1), nrow = 6)
epsilon_1 <- rnorm(100, 0, 1)
epsilon_2 <- rnorm(100, 0, 1)

Y_1 <- X_1%*%Beta_1 + epsilon_1
Y_2 <- X_2%*%Beta_2 + epsilon_2

Y <- rbind(Y_1, Y_2)
X <- rbind(X_1, X_2)
```

```{r}
df_simulated <- cbind(Y, X) %>% 
  as.data.frame()

colnames(df_simulated) <- c("Y", "const", "X1", "X2", "X3", "X4", "X5")

df_simulated %>% 
  head()
```

```{r}
df_simulated %>% 
  write.csv("simulation_data_R.csv", row.names = FALSE)
```


```{r}
df_simulated %>% 
  mutate(time = row_number()) %>% 
  ggplot(mapping = aes(x = time, y = Y)) +
  geom_line()
```



## Benchmark Methods:



### Bai and Perron (2003)

- `breakpoints()` from [strucchange](https://cran.r-project.org/web/packages/strucchange/strucchange.pdf)
  - `breaks = `: maximal number of change points for detecting
  - `h = `: minimal segment size either given as fraction relative to the sample size or as an integer giving the minimal number of observations in each segment.
  
  
  
  
```{r}
result_Bai_Perron <- breakpoints(Y ~ X1 + X2 + X3 + X4 + X5, data = df_simulated, breaks = 5, h = 0.15)
result_Bai_Perron
```

```{r}
summary(result_Bai_Perron)
```


- BIC is used as criteria to choose the number of change points

```{r}
result_Bai_Perron %>% plot()
```




### Wang and Emerson (2015); Barry and Hartigan (1993): Bayesian approach

- `bcp()` from [bcp](https://cran.r-project.org/web/packages/bcp/bcp.pdf) package

```{r}
result_bcp <- bcp(y = Y, x = X, p0 = 1, nreg = 3)
plot(result_bcp)
```

<!-- ### Muggeo (2003) -->

<!-- - `segmented()` from [segmented](https://cran.r-project.org/web/packages/segmented/segmented.pdfted) -->

<!-- - I am not sure what `seg.Z` means. Document says `seg.Z` is the segmented variable, i.e. the continuous covariates understood to have a piecewise-linear relationship will be estimated -->


```{r}
# model_lm <- lm(Y ~ 1, data = df_simulated)
# segmented(model_lm, seg.Z =  ~ X1 + X2 + X3 + X4 + X5) %>% plot(term = X1)
```



```{r}
# df_simulated <- mutate(df_simulated,
#                        time = row_number())
# model_lm <- lm(Y ~ X1 + X2 + X3 + X4 + X5, data = df_simulated)
# segmented(model_lm, seg.Z =  ~ time) %>% plot()
```

```{r}
# df_simulated <- mutate(df_simulated,
#                        time = row_number())
# model_lm <- lm(Y ~ time, data = df_simulated)
# segmented(model_lm, seg.Z = ~ X1 + X2 + X3 + X4 + X5) %>% summary()
```

```{r}
# model_lm <- lm(Y ~ X1 + X2 + X3 + X4 + X5, data = df_simulated)
# segmented(model_lm, seg.Z =   ~ X1 + X2 + X3 + X4 + X5) %>% plot(term = "X1")
```



## Simulated data: multiple (3) change points

```{r}
set.seed(123)
X_const <- matrix(rep(1, 100), nrow = 100)
X_1 <- mvrnorm(n = 100, mu = rep(0, 5), Sigma = diag(5))
X_2 <- mvrnorm(n = 100, mu = rep(0, 5), Sigma = diag(5))
X_3 <- mvrnorm(n = 100, mu = rep(0, 5), Sigma = diag(5))
X_4 <- mvrnorm(n = 100, mu = rep(0, 5), Sigma = diag(5))

X_1 <- cbind(X_const, X_1)
X_2 <- cbind(X_const, X_2)
X_3 <- cbind(X_const, X_3)
X_4 <- cbind(X_const, X_4)

Beta_1 <- matrix(rep(1, 6), nrow = 6)
Beta_2 <- matrix(c(1, -1, 0, -1, 0, 1), nrow = 6)
Beta_3 <- matrix(c(1, 0, 1, 1, 0, -1), nrow = 6)
Beta_4 <- matrix(c(1, 1, 0, -1, -1, 1), nrow = 6)

epsilon_1 <- rnorm(100, 0, 1)
epsilon_2 <- rnorm(100, 0, 1)
epsilon_3 <- rnorm(100, 0, 1)
epsilon_4 <- rnorm(100, 0, 1)

Y_1 <- X_1%*%Beta_1 + epsilon_1
Y_2 <- X_2%*%Beta_2 + epsilon_2
Y_3 <- X_3%*%Beta_3 + epsilon_3
Y_4 <- X_4%*%Beta_4 + epsilon_4

Y_multi <- rbind(Y_1, Y_2, Y_3, Y_4)
X_multi <- rbind(X_1, X_2, X_3, X_4)
```

```{r}
df_simulated_multi <- cbind(Y_multi, X_multi) %>% 
  as.data.frame()

colnames(df_simulated_multi) <- c("Y", "const", "X1", "X2", "X3", "X4", "X5")

df_simulated_multi %>% 
  head()
```

## Benchmark Methods:

### Bai and Perron (2003)

```{r}
result_Bai_Perron_multi <- breakpoints(Y ~ X1 + X2 + X3 + X4 + X5, data = df_simulated_multi)
result_Bai_Perron_multi
```

```{r}
summary(result_Bai_Perron_multi)
```


```{r}
result_Bai_Perron_multi %>% plot()
```

### Wang and Emerson (2015); Barry and Hartigan (1993): Bayesian approach

```{r}
result_bcp_multi <- bcp(y = Y_multi, x = X_multi)
plot(result_bcp_multi)
```








